magGen: Generator of Static Evaluators for Multi-plans Attribute Grammars.\par
%  \href{http://code.google.com/p/genevalmag/}{\tt http://code.google.com/p/genevalmag/}\par
 Copyright\textcopyright 2010 Kilmurray - Picco\par

\textit{Departamento de Computaci\'on\\
        Facultad de Ciencias Exactas, F\'isico-Qu\'imicas y Naturales\\
        Universidad Nacional de R\'io Cuarto\\
        C\'ordoba - Argentina}

System: magGen\par
 Homepage: $<$\href{http://code.google.com/p/genevalmag/}{\tt http://code.google.com/p/genevalmag/}$>$\par
 Language: C++\par
 \par
%  Authors: Kilmurray, Gerardo Luis\par
%  Authors: Picco, Gonzalo Martín\par
%  E-Mail: gerakilmurray@gmail.com\par
%  E-Mail: gonzalopicco@gmail.com\par
%  \par
 magGen is free software: you can redistribute it and/or modify\par
 it under the terms of the GNU General Public License as published by\par
 the Free Software Foundation, either version 3 of the License, or\par
 (at your option) any later version.\par


 magGen is distributed in the hope that it will be useful,\par
 but WITHOUT ANY WARRANTY; without even the implied warranty of\par
 MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE. See the\par
 GNU General Public License for more details.\par


 You should have received a copy of the GNU General Public License\par
 along with magGen. If not, see $<$\href{http://www.gnu.org/licenses/}{\tt http://www.gnu.org/licenses/}$>$.\par


\begin{Desc}
\item [Director:] Arroyo, Marcelo Daniel
\vspace*{0.8cm}

\item[Author:]Kilmurray, Gerardo Luis $<$\href{mailto:gerakilmurray@gmail.com}{\tt gerakilmurray@gmail.com}$>$ 

Picco, Gonzalo Mart\'in $<$\href{mailto:gonzalopicco@gmail.com}{\tt gonzalopicco@gmail.com}$>$\end{Desc}
\begin{Desc}
\item[Date:]June 2010\end{Desc}
\hypertarget{index_intro}{}\section{Introduction}\label{index_intro}
% Trabajo realizado en el marco de la Tesis de Licenciatura en Ciencias de la Computación.
Work done as part of the Thesis of Bachelor of Computer Science.

SVN repository:\par
\par
$<$\href{http://code.google.com/p/genevalmag/}{\tt http://code.google.com/p/genevalmag/}$>$
\par
% En este repositorio podrá encontrar:\par
In this repository you will find:\par
\begin{itemize}
% \item bin: Contiene el binario de maggen y archivos necesarios para la generación del evaluador.
\item bin: Contains the binary files needed to magGen and evaluator generation.

% \item doc: Contiene toda la documentación y tutoriales de la herramienta.
\item doc: It contains all the documentation and tutorials of the tool.

% \item include: Contiene las cabeceras para incluir los archivos que permiten parsing y analisis de MAG, generación de grafos, planes y secuencias de visitas.
\item include: It contains the headers to include the files that make parsing and analysis of MAG, generating graphs, plans and sequences of visits.

% \item src: Contiene todos los archivos de implementación de la herramienta.
\item src: Contains files for implementing the tool.

% \item examples: Contiene ejemplos para ver el funcionamiento de maggen.
\item examples: It contains examples for operation of maggen.

% \item scripts: Contiene scripts en bash para convertir archivos .dot en imágenes PNG.
\item scripts: Contains bash scripts to convert dot files in PNG images.

\end{itemize}


% Enlaces principales: \href{http://code.google.com/p/genevalmag/}{\tt Genevalmag GoogleCode }

% \hypertarget{index_notes}{}
% \section{Notas}\label{index_notes}
% En etapa de escritura del informe

\hypertarget{index_requirements}{}
\section{Requirements}\label{index_requirements}
% Para compilar la herramienta magGen, se necesita:
To compile maggen tool you need:
\begin{itemize}
\item Boost C++ Libraries >= 1.41 $<$\href{http://www.boost.org/}{\tt http://www.boost.org/}$>$
\item g++ >= 4.3.3
\end{itemize}

\par
\par
 